Causal_Analysis_Paper

### 2022-05-29 PaperAnalysis.Rmd
Added references of the datasets to the Rmd file.

## Description of the original paper
Latt, Milner and Kavanagh present the results of their ecological study on the effects of abortion laws on maternal mortality in their paper "Abortion laws reform may reduce maternal mortality: an ecological study in 162 countries."

### Datasets
The authors used a time-indexed dataset of maternal mortality from 1985 to 2015

To assess the effect of flexibility of abortion laws on on maternal mortality, the authors create an aggregate flexibility index [1-7] calculated based on the sum of the grounds on which abortion is permitted in every country

Description of Covariates.

##    Causal Design of the original paper

@@

-

>>>>

## Description of the original paper

##  The causal design of the original paper

@@

- WHO. (2022). Maternal Mortality Database.[Accessible here:](https://platform.who.int/mortality/themes/theme-details/topics/topic-details/MDB/maternal-conditions)
